Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-02 article.tex
bookmark

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} of the particle. For an
aerosol, the single scattering albedo is denoted $\varpi^{\rm
  aerosol}$.  The {\em scattering coefficient} due to aerosols in the
volume is
\begin{align}
  \alpha^{\rm aerosol}= \varpi^{\rm aerosol}\beta^{\rm aerosol}
  =\varpi^{\rm aerosol} \sigma^{\rm aerosol} n \;.
  \label{eq:alph}
\end{align}
The angular distribution of scattering by an aerosol is determined by
a {\em phase function} $P^{\rm aerosol}$, which is normalized: its
integral over all solid angles is unit. Part of the light scatters
towards a camera's LOS, as illustrated in \cref{fig:groundgrid}. The
angle between the SR and LOS is the scattering angle $\Phi^{\rm
  scatter}$. The {\em angular scattering coefficient} due to aerosols
is
\begin{align}
  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter}) = \alpha^{\rm
    aerosol} P^{\rm aerosol}(\Phi^{\rm scatter}) = \varpi^{\rm
    aerosol} \sigma^{\rm aerosol} n P^{\rm aerosol}(\Phi^{\rm
    scatter}).
  \label{eq:alphabasic}
\end{align}
The phase function is often approximated by a parametric
expression. Specifically, the Henyey-Greenstein~\cite{Cornette1995}
function is governed by an {\em anisotropy parameter} $g$:
\begin{align}
  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -
  g^2)(1+\mu^2)}{(2+g^2)(1 + g^2 - 2g\mu)^{\sfrac{3}{2}}}
  \label{eq:aerosol_scatter}
\end{align}
\hl{where $\mu\equiv \cos \Phi^{\rm scatter}$}

@@

As illustrated in \cref{fig:groundgrid,fig:distributions},
The sky is discretized into a grid of $N_{\rm voxels}$ \fix{volume
  elements}{rectangular cuboid elements}
(voxels), indexed by $k$, $m$ or $q$.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small Simulated 3D aerosol distributions: [a] {\em Haze
      blobs} and [b] {\em Haze Front}.  Here, an aerosol density unit
    is $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
    area of $50\times 50{\rm km}^2$, extending from the ground up to
    altitude of 10km. The domain is divided into a rectilinear grid
    having $N_{\rm voxels}$ voxels.}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense: inside fog and clouds this model does not
apply. In this model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
To demonstrate the model, we simulated some scenarios, whose details are as follows.
\\

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}(a)):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.}
  \label{fig:mcgrid}
\end{figure}

@@

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~(\ref{eq:aerosol_scatter})
or~(\ref{eq:rayleighP})). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
Estimation~\cite{marshak20053d} is used for calculating the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].
Comparison of \hl{horizontal and vertical cross sections along 
matching MC and single-scattering simulated images are} shown in
\cref{fig:cross_sections}(a) and \cref{fig:cross_sections}(b).
\hl{The cross sections indicate fair correspondence between
the MC and single-scattering simulations.}
\begin{figure}[th]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross sections along the $X$-Axis [a] and $Y$-Axis [b] of
    a MC and single-scattering simulations. Overlay of the cross
    sections on the MC simulated image is shown in [c]. }
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
scattering events to the MC image. The amount of light scattered
in the direction of the sun due to the first scatter event of each photon
is collected to create} \cref{fig:scatter_order}(a). \hl{This process
is repeated for the second and third scatter events creating}
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
\hl{respectively. It is conspicuous that the first scatter is responsible
for most of the energy in the MC image. The effect of subsequent scatters
is mostly evident at the horizon. The line of sight extending into the
horizon crosses a larger volume of atmosphere then the line of sight extending
in the direction of the zenith. This increases the probability of
scattering events along the line of sight extending into the horizon.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of a MC simulated image to (a) first
   scattering order, (b) second scattering order and (c) third
   scattering order. }
  \label{fig:scatter_order}
\end{figure}

@@

When the type of aerosol above an area is known~\cite{Martonchik2009},
estimation of the density distribution $\DistUnknown$ is needed. The
data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
optimization of a cost function that fits the image-formation model to
the data. Let $\DistSet$ be the set of all distributions complying
with some constraints.  Particularly, $\DistUnknown$ is non-negative,
and its spatial support is bounded between the ground and the TOA. The
optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\|
    \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2  + \eta \Psi({\bm n}).
\end{equation}
Here $\MaskSun$ masks the area around the sun, as in real-world images
it is indeed blocked. \hl{It is also used for masking the areas in the image
prone for multiple scattering events, e.g. the horizon area as evident in}
\cref{fig:scatter_order}(b).  In \cref{eq:objectiveA}, $\Psi({\bm n})$
is a regularization term that expresses some prior knowledge on the
distribution, while $\eta$ is the regularization weight.

@@

\section{Results}
\label{sec:optimization-results}

\Cref{sec:simul} describes simulated scenes at various grid
resolutions.  Depending directly on the area grid finesse, $N_{\rm
  views}$ varied from 12 to 100.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    single-scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
We applied the reconstruction algorithm to images created as described
in \cref{sec:simul,sec:monte-carlo-simul}. We used the
L-BFGS-B algorithm~\cite{BFGS} on a computer cluster. Each core was
dedicated to rendering a modeled image. The algorithm was initialized
by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
iterations. Depending on the resolution it took between minutes to a
couple of hours to complete, in total.

\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}. 
\hl{
In these simulations the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Thirty six cameras were placed
$\sim7$km apart on a $6\times6$ grid.
}
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both
in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}. The total estimation
error can be quantified by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
The overall mass is recovered, but for 6.5\% loss. For local errors,
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
$\epsilon=0.65$.

\hl{Optimal placement of cameras is an important aspect in realization
of the suggested system. As a first step we would like to measure the effect of
the distance between the cameras on the estimation quality. For this, we
repeated the reconstruction algorithm, each time using a subset of varying size
of the raw images. In each test the reconstruction algorithm was applied to $n_{views}$
($<N_{views}$) images. The images were selected randomly from the total $N_{views}$ raw images.
To eliminate the effect of incidental camera position, the test was repeated several
times each time with a different $n_{views}$ subset.} \Cref{fig:error_vs_cameras}
\hl{summarizes the results of these tests. In can be seen that a good estimation
is achieved already when using $20$ cameras. Over an area of $50\times 50{\rm km}^2$,
this quantity relates to placing the cameras $\sim11$km apart.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small Local error measure as function of cameras
    quantity. The blue error bars represent the error standard
    deviation. The dashed horizontal line marks the reconstruction
    error when all thirty six cameras are used.}
  \label{fig:error_vs_cameras}
\end{figure}

\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
This admits to the fact that the single-scattering model, on which the reconstruction
algorithm is based, is valid when the optical depth of the medium is small.}
% \begin{figure}[h]
%   \centering
%   \yoavcomment{\includegraphics{images/high_density_results.pdf}}
%   \caption{\small (a) and (b) show MC simulations of low and 
%     high density scenes, respectively. (c) shows the reconstruction of
%     the high density scene.}
%   \label{fig:high_density}
% \end{figure}

>>>>

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} of the particle. For an
aerosol, the single scattering albedo is denoted $\varpi^{\rm
  aerosol}$.  The {\em scattering coefficient} due to aerosols in the
volume is
\begin{align}
  \alpha^{\rm aerosol}= \varpi^{\rm aerosol}\beta^{\rm aerosol}
  =\varpi^{\rm aerosol} \sigma^{\rm aerosol} n \;.
  \label{eq:alph}
\end{align}
The angular distribution of scattering by an aerosol is determined by
a {\em phase function} $P^{\rm aerosol}$, which is normalized: its
integral over all solid angles is unit. Part of the light scatters
towards a camera's LOS, as illustrated in \cref{fig:groundgrid}. The
angle between the SR and LOS is the scattering angle $\Phi^{\rm
  scatter}$. The {\em angular scattering coefficient} due to aerosols
is
\begin{align}
  \tilde\alpha^{\rm aerosol}(\Phi^{\rm scatter}) = \alpha^{\rm
    aerosol} P^{\rm aerosol}(\Phi^{\rm scatter}) = \varpi^{\rm
    aerosol} \sigma^{\rm aerosol} n P^{\rm aerosol}(\Phi^{\rm
    scatter}).
  \label{eq:alphabasic}
\end{align}
The phase function is often approximated by a parametric
expression. Specifically, the Henyey-Greenstein~\cite{Cornette1995}
function is governed by an {\em anisotropy parameter} $g$:
\begin{align}
  P^{\rm aerosol}_g(\Phi^{\rm scatter})\approx \frac{3}{8\pi} \frac{(1 -g^2)
  [1+(\cos \Phi^{\rm scatter})^2]}
  {(2+g^2)(1 + g^2 - 2g\cos \Phi^{\rm scatter})^{\sfrac{3}{2}}}
  \label{eq:aerosol_scatter}
\end{align}

@@

As illustrated in \cref{fig:groundgrid,fig:distributions},
The sky is discretized into a grid of $N_{\rm voxels}$ rectangular cuboid volume elements
(voxels), indexed by $k$, $m$ or $q$.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small Simulated 3D aerosol distributions: [a] {\em Haze
      blobs} and [b] {\em Haze Front}.  Here, an aerosol density unit
    is $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
    area of $50\times 50{\rm km}^2$, extending from the ground up to
    altitude of 10km. The domain is divided into a rectilinear grid
    having $N_{\rm voxels}$ voxels.}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense: inside fog and clouds this model does not
apply. In this model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

To demonstrate the model, we simulated some scenarios, whose details are as follows.
\\

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}.

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}a):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.}
  \label{fig:mcgrid}
\end{figure}

@@

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
Estimation~\cite{marshak20053d} is used for calculating the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].
Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
cross sections of the viewed field, extracted from the images in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).
These plots demonstrate consistency in these cases, for most pixels.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross sections along the $X$-axis [a] and $Y$-axis [b] of
    and images rendered by either single-scattering and MC. The corresponding
    images appear in \cref{fig:simulation-results1}[left] and \cref{fig:mcgrid}(b).}
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing to an image pixel are accumulated in steps {\tt ii},{\tt v} above.
The contributing photons that stem from just a single scattering event yield \cref{fig:scatter_order}(a). Similarly, contributing photons that had experienced exactly  two or three scattering events yield respectively \cref{fig:scatter_order}(b) and
\cref{fig:scatter_order}(c). Clearly, first-order scatter is responsible
for most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long and dense part of the atmosphere, while a vertical LOS cuts short through the dense, lower part. Hence,
towards the horizon the probability of high order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contribution by successive orders of scattering: (a) first  order, (b) second order and (c) third scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

When the type of aerosol above an area is known~\cite{Martonchik2009},
estimation of the density distribution $\DistUnknown$ is needed. The
data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
optimization of a cost function that fits the image-formation model to
the data. Let $\DistSet$ be the set of all distributions complying
with some constraints.  Particularly, $\DistUnknown$ is non-negative,
and its spatial support is bounded between the ground and the TOA. The
optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\|
    \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2  + \eta \Psi({\bm n}).
\end{equation}
Here $\MaskSun$ masks the area around the sun, as in real-world images
it is indeed blocked. We mask the horizon, by using a camera whose field of view is a bit smaller than hemispherical. This reduces the influence of image regions that are more strongly affected by high-order scattering (\cref{fig:scatter_order}(b)). Consequently,
the fit of the image formation model focuses on the bulk image region, where the single scattering model is more valid.  In \cref{eq:objectiveA}, $\Psi({\bm n})$
is a regularization term that expresses some prior knowledge on the
distribution, while $\eta$ is the regularization weight.

@@

\section{Recovery simulations}
\label{sec:optimization-results}

To demonstrate recovery, we performed simulations. We tested how results are affected by the following variations:
$\{1\}$ Multiple or only single scatter in the forward model;
$\{2\}$ Spatial distribution;
$\{3\}$ Density of viewpoints;
$\{4\}$ Aerosol characteristics;
$\{5\}$ Density scale.

In all cases, images were created as described
in \cref{sec:simul,sec:monte-carlo-simul}. These images served as input to the reconstruction algorithm. The optimization used an L-BFGS-B solver~\cite{BFGS} on a computer cluster. Each computer core was dedicated to rendering a modeled image. The algorithm was initialized
by ${\bm n}=0$.  Satisfactory convergence occurred in several hundred
iterations. Depending on the resolution it took between minutes to a
couple of hours to complete, in total. The total estimation
error can be quantified by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm,
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$. 
To also sense local errors, we use 
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
%  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
%$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
%$\epsilon=0.65$.
These results are listed in Table~\ref{tbl:mass}. \\

\noindent{\bf Forward models and distributions}: 
\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}.
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/results}}
  \caption{\small Reconstructions of the scenes shown in
    \cref{fig:distributions}. Color represents aerosol density. The
    density units are $10^{6}~{\rm particles}/{\rm m}^3.$ In [a,b],
    single-scattering simulated images are used as input to the
    recovery.  In [c,d], MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
\hl{
In these simulations the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Thirty six cameras were placed
$\sim7$km apart on a $6\times6$ grid.
}
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}.
The overall mass is recovered, but for 6.5\% loss. \\

% at various grid
%resolutions.  Depending directly on the area grid finesse, $N_{\rm
%  views}$ varied from 12 to 100.
%
%
%For local errors,
% $\epsilon=\|
%\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
%  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
%$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
%$\epsilon=0.65$.

\noindent{\bf Density of viewpoints}: Keeping the domain and scene ({\em Haze blobs}) fixed, we
repeated the reconstruction many times, each time using a different subset of the above mentioned 36 simulated cameras. Each test randomly selected viewpoints, for various fixed values
of $N_{\rm views}< 36$. All rendered images used MC.
\Cref{fig:error_vs_cameras} plots $\epsilon$ as a function $N_{\rm views}$. 
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small Relative error $\epsilon$ measure as function of the number of
    cameras. Bars represent the standard deviation of $\epsilon$, over our random tests.}
  \label{fig:error_vs_cameras}
\end{figure}
Diminishing returns are obtained beyond $N_{\rm views}\approx 20$, which corresponds to $\approx 11$km separation between neighboring viewpoints.\\

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the  
aerosol characteristics. Compared to the aerosol described in Sec.~\ref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e., 
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is 
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC, and recovery used $N_{\rm views}=36$.
Sample results are shown in Fig.~\ref{fig:variations}(a,b,c,d) and in Table~\ref{tbl:mass}.\\

\noindent{\bf Density scale}: We used the aerosol {\em Haze blobs} distribution and characteristics as described in Sec.~\ref{sec:simul}, but increased the aerosol density tenfold everywhere. This significantly increases the effects of high order scattering, as shown in Fig.~\ref{fig:cross_sections}(b) and Fig.~\ref{fig:variations}(e). Consequently, $\epsilon$ increases, when using $N_{\rm views}=36$. Still, Fig.~\ref{fig:variations}(f) shows that the spatial distribution outlines are recovered similarly to the other tests.

%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
%This admits to the fact that the single-scattering model, on which the reconstruction
%algorithm is based, is valid when the optical depth of the medium is small.}
% \begin{figure}[h]
%   \centering
%   \yoavcomment{\includegraphics{images/high_density_results.pdf}}
%   \caption{\small (a) and (b) show MC simulations of low and
%     high density scenes, respectively. (c) shows the reconstruction of
%     the high density scene.}
%   \label{fig:high_density}
% \end{figure}
